{\bf Landslide: A New Race-Finding Tool for 15-410}

### 2018-02-16 landslide-lecture/2018/lecture.tex
upd lecture for s18

\institute[CMU 15-410]{Carnegie Mellon University - 15-410}
\date[]{2017, September 27}

@@

\begin{frame}{Case Study}
	\begin{center}
		\begin{tabular}{llll}
			\fbox{
			\begin{tabular}{l}
				Consumer thread \\
				\hline
				\\
				\texttt{mutex\_lock(mx);} \\
				\\
				\texttt{if~(!work\_exists())} \\
				\texttt{~~~~cond\_wait(cvar,~mx);} \\
				\texttt{work~=~dequeue();} \\
				\\
				\texttt{mutex\_unlock(mx);} \\
				\texttt{access(work->data);} \\
			\end{tabular}
			}
			& & &
			\fbox{
			\begin{tabular}{l}
				Producer thread \\
				\hline
				\\
				\texttt{mutex\_lock(mx);} \\
				\\
				\texttt{enqueue(work);} \\
				\texttt{signal(cvar);} \\
				\\
				\texttt{mutex\_unlock(mx);} \\
				\\
				\\
			\end{tabular}
			}
		\end{tabular}
		\linegap

@@

\begin{frame}{Testing}
	How can programmers be confident in the correctness of their code?
	\begin{itemize}
		\item Unit tests
		\begin{itemize}
			\item good for basic functionality, bad for concurrency
		\end{itemize}
		\item Stress tests
		\begin{itemize}
			\item state of the art in 15-410
		\end{itemize}
		\item Theorem proving
		\begin{itemize}
			\item heavy burden on the programmers
		\end{itemize}
		\item Releasing to paying customers and worrying about correctness later
			% Say... "and I'm hoping to prevent you from finding yourself in a future where this happens!"
	\end{itemize}
	\linegap

@@

\begin{frame}{About The Project}
	\textbf{About me}: Final(?) year graduate student, advised by Garth Gibson
	\begin{itemize}
		\item TAed 15-410 for 3 semesters during undergrad
		%\item 1st graduate year was 5th year M.S., rest in Ph.D. program
		\item Landslide's publication history
		\begin{itemize}
			\item Master's thesis
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/thesis.pdf}
			\end{itemize}
			\item Conference paper (OOPSLA 2016)
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/oopsla.pdf}
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Previous Semesters}
	%% S'15, F'15, S'16: 48 groups signed up to use Landslide; 38 found bugs
	S'15, F'15, S'16, F'16, S'17: 79 groups signed up to use Landslide; 59 found bugs
	\linegap

	%%44 {\em deterministic} bugs (e.g. swexn, initialization)
	91 {\em deterministic} bugs (e.g. swexn, initialization)
	\linegap

	%%85 distinct {\em non-deterministic} bugs (among 32 groups)
	113 distinct {\em non-deterministic} bugs (among 44 groups)
	\begin{itemize}
		\item 33 groups (75\%) fixed $\ge 1$ such bug
		%%\item 24 groups (75\%) fixed $\ge 1$ such bug
			\begin{itemize}
				\item (as verified by running Landslide again -- not a guarantee!)
			\end{itemize}
		\item 24 groups (55\%) fixed {\em all} such bugs
		%%\item 15 groups (47\%) fixed {\em all} such bugs
		\item Most ambitious group: 11 distinct races found + fixed!
	\end{itemize}
	\linegap
\end{frame}

>>>>

\institute[CMU 15-410]{Carnegie Mellon University - 15-410}
\date[]{2018, February 16}

@@

\begin{frame}{Case Study}
	\begin{center}
		\begin{tabular}{llll}
			\fbox{
			\begin{tabular}{l}
				Consumer thread \\
				\hline
				\\
				\texttt{mutex\_lock(mx);} \\
				\\
				\texttt{if~(!work\_exists())} \\
				\texttt{~~~~cond\_wait(cvar,~mx);} \\
				\texttt{work~=~dequeue();} \\
				\\
				\texttt{mutex\_unlock(mx);} \\
				\texttt{access(work->data);} \\
			\end{tabular}
			}
			& & &
			\fbox{
			\begin{tabular}{l}
				Producer thread \\
				\hline
				\\
				\texttt{mutex\_lock(mx);} \\
				\\
				\texttt{enqueue(work);} \\
				\texttt{signal(cvar);} \\
				\\
				\texttt{mutex\_unlock(mx);} \\
				\\
				\\
			\end{tabular}
			}
		\end{tabular}
		\pause
		\linegap

@@

\begin{frame}{Testing}
	How can programmers be confident in the correctness of their code?
	\begin{itemize}
		\item Unit tests
		\begin{itemize}
			\item good for basic functionality, bad for concurrency
		\end{itemize}
		\item Stress tests
		\begin{itemize}
			\item state of the art in 15-410
		\end{itemize}
		\item Theorem proving
		\begin{itemize}
			\item heavy burden on the programmers
		\end{itemize}
		\item \sout{Releasing to paying customers and worrying about correctness later}
			% Say... "and I'm hoping to prevent you from finding yourself in a future where this happens!"
	\end{itemize}
	\linegap

@@

\begin{frame}{About The Project}
	\textbf{About me}: Final year graduate student, advised by Garth Gibson
	\begin{itemize}
		\item TAed 15-410 for 3 semesters during undergrad
		%\item 1st graduate year was 5th year M.S., rest in Ph.D. program
		\item Landslide's publication history
		\begin{itemize}
			\item Master's thesis
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/thesis.pdf}
			\end{itemize}
			\item Conference paper (OOPSLA 2016)
			\begin{itemize}
				\item \url{http://www.contrib.andrew.cmu.edu/~bblum/oopsla.pdf}
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Previous Semesters}
	%% S'15, F'15, S'16: 48 groups signed up to use Landslide; 38 found bugs
	%% S'15, F'15, S'16, F'16, S'17: 79 groups signed up to use Landslide; 59 found bugs
	S'15, F'15, S'16, F'16, S'17, F'17: 94 groups signed up to use Landslide; 71 found bugs
	\linegap

	%%44 {\em deterministic} bugs (e.g. swexn, initialization)
	%% F17 lecture - stats up to S17
	%% 91 {\em deterministic} bugs (e.g. swexn, initialization)
	% S18 lecture - stats up to F17
	109 {\em deterministic} bugs (e.g. swexn, initialization)
	\linegap

	%%85 distinct {\em non-deterministic} bugs (among 32 groups)
	%% F17 lecture - stats up to S17
	%% 113 distinct {\em non-deterministic} bugs (among 44 groups)
	% S18 lecture - stats up to F17
	122 distinct {\em non-deterministic} bugs (among 49 groups)
	\begin{itemize}
		\item 36 groups (73\%) fixed $\ge 1$ such bug
		%\item 33 groups (75\%) fixed $\ge 1$ such bug
		%%\item 24 groups (75\%) fixed $\ge 1$ such bug
			\begin{itemize}
				\item (as verified by running Landslide again -- not a guarantee!)
			\end{itemize}
		\item 26 groups (53\%) fixed {\em all} such bugs
		%\item 24 groups (55\%) fixed {\em all} such bugs
		%%\item 15 groups (47\%) fixed {\em all} such bugs
		\item Most ambitious group: 11 distinct races found + fixed!
	\end{itemize}
	\linegap
\end{frame}
